Multi-target detection with application to cryo-electron microscopy

### 2019-03-01 inverse_problems/inverse_problems.tex
section 3.1

Under the separation condition~\eqref{eq:spacing}, the relation between autocorrelations of the observation $y$ and those of $x$ is particularly simple, as we now show. It is useful to introduce some notation: let $\vert s\vert = \sum_i s[i]$ denote the number of signal occurrences in $y$, and let
\begin{equation}
\gamma  = \frac{|s| L}{N}.
\label{eq:gamma}
\end{equation}
This $\gamma$ is the fraction of entries of $y$ occupied by signal occurrences. Henceforth, we call it the signal density.
The separation condition  imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.

@@

\TODO{We show in Section~\ref{sec:theory_homogeneous} how to estimate $\gamma$ from observations for the particular case where $K = 1$ (all signal occurrences are the same).}

>>>>

Under the separation condition~\eqref{eq:spacing}, the relation between autocorrelations of the observation $y$ and those of $x$ is particularly simple, as we now show. It is useful to introduce some notation: let $\vert s\vert = \sum_i s[i]$ denote the number of signal occurrences in $y$, and let
\begin{equation}
\gamma  = \frac{|s| L}{N}.
\label{eq:gamma}
\end{equation}
This $\gamma$ is the fraction of entries of $y$ occupied by signal occurrences. %Henceforth, we call it the signal density.
The separation condition  imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.

@@

We show in Section~\ref{sec:theory_homogeneous} 
that $x,\gamma$ and $\sigma$ can be identified uniquely from the autocorrelations for the particular case where $K = 1$ (all signal occurrences are the same).
